Headgroup Structure and Cation Binding in Phosphatidylserine Lipid Bilayers

### 2019-09-03 Manuscript/manuscriptPS.tex
Acknowledgements

\begin{acknowledgement}
  MJ acknowledges financial support from the Emil Aaltonen foundation and
  and CSC-IT center for science for computational resources.
  JJM gratefully acknowledges financial support from the Carlsberg Foundation in the form of a postdoctoral fellowship while at the University of Chicago (grants CF15-0552, CF16-0639, and CF17-0783) and the research framework provided by the Research Computing Center at the University of Chicago.
  OHSO acknowledges financial support from Academy of Finland (315596),
  Integrated Structural Biology Research Infrastructure of
  Helsinki Institute of Life Science (Instruct-HiLIFE), and
  CSC-IT center for science for computational resources.
  TJP wishes to acknowledge the use of the Iridis computing resources at the University of Southampton.
  FFR acknowledges Tecnol\'{o}gico Nacional de M\'{e}xico Campus Zacatecas Occidente and
  Direcci\'{o}n General de Asuntos del Personal Acad\'{e}mico (DGAPA)
  Programa de Apoyo a Proyectos de Investigaci\'{o}n e Innovaci\'{o}n
  Tecnol\'{o}gica (PAPIIT) IG100416 for financial support and Cl\'{u}ster
  H\'{i}brido de Superc\'{o}mputo Xiuhcoatl-CINVESTAV and Miztli-Direcci\'{o}n de
  C\'{o}mputo y de Tecnolog\'{i}as de Informaci\'{o}n y Comunicaci\'{o}n (DGTIC)-
  Universidad Nacional Aut\'{o}noma de M\'{e}xico (UNAM) (Project
  LANCAD-UNAM-DGTIC-028) facilities for computing-time allocation.
\end{acknowledgement}

>>>>

\begin{acknowledgement}
  HA acknowledges the Osk. Huttunen Foundation and the Finnish Academy of Science and Letters (Foundations' Post Doc Pool) for financial support.
  FFR acknowledges Tecnol\'{o}gico Nacional de M\'{e}xico Campus Zacatecas Occidente and
  Direcci\'{o}n General de Asuntos del Personal Acad\'{e}mico (DGAPA)
  Programa de Apoyo a Proyectos de Investigaci\'{o}n e Innovaci\'{o}n
  Tecnol\'{o}gica (PAPIIT) IG100416 for financial support and Cl\'{u}ster
  H\'{i}brido de Superc\'{o}mputo Xiuhcoatl-CINVESTAV and Miztli-Direcci\'{o}n de
  C\'{o}mputo y de Tecnolog\'{i}as de Informaci\'{o}n y Comunicaci\'{o}n (DGTIC)-Universidad Nacional Aut\'{o}noma de M\'{e}xico (UNAM) (Project
  LANCAD-UNAM-DGTIC-028) facilities for computing-time allocation.
  MJ acknowledges financial support from the Emil Aaltonen Foundation
  and CSC -- IT Center for Science for computational resources.
  JJM gratefully acknowledges financial support from the Carlsberg Foundation in the form of a postdoctoral fellowship while at the University of Chicago (grants CF15-0552, CF16-0639, and CF17-0783) and the research framework provided by the Research Computing Center at the University of Chicago.
  OHSO acknowledges financial support from Academy of Finland (315596),
  Integrated Structural Biology Research Infrastructure of
  Helsinki Institute of Life Science (Instruct-HiLIFE), and
  CSC -- IT Center for Science for computational resources.
  TJP wishes to acknowledge the use of the Iridis computing resources at the University of Southampton.
\end{acknowledgement}
